---
title: "simulation"
author: "Emily Potts"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

set.seed(1)
```

# simulaton: mean & SD for one n

```{r}
sim_mean_sd = function(n, mu = 7, sigma = 4) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

how did we use this before?
```{r}
sim_mean_sd(n = 30)
```

how can we use this now?

let's start with a for loop
```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  
  output[[i]] = sim_mean_sd(n = 30)
}

sim_results = bind_rows(output)
```

let's use list columns instead
```{r}
sim_results_df = 
  expand_grid(
  sample_size = 30,
  iteration = 1:100
) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

plots describing simulations results
```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) + geom_density()
```

```{r}
sim_results_df %>% 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter) %>% 
  summarize(
    emp_mean = mean(estimate),
    emp_sd = sd(estimate)) %>% 
  knitr::kable(digits = 3)
```

# simulaton: mean for several ns
what about changing the sample size?
```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iteration = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
sim_results_df
```

plot comparing distributions of mean estimates across sample sizes
```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()
```

looking at empirical mean & variance of these estimates
```{r}
sim_results_df %>% 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, sample_size) %>% 
  summarize(
    emp_mean = mean(estimate),
    emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)
```

# varying two simulation parameters
```{r, cache=TRUE}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    true_sigma = c(6, 3),
    iteration = 1:100
  ) %>% 
  mutate(
    estimate_df = map2(.x = sample_size, .y = true_sigma, ~sim_mean_sd(n = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)
sim_results_df
```

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() + 
  facet_grid(. ~ true_sigma)
```

